---
title: 'Introduction to dplyr 1.0.0 : Exercises'
author: "Mine Kara"
date: "October 17, 2021"
output: 
  rmdformats::downcute:
    self_contained: true
    default_style: "light"
    downcute_theme: "default"
    code_folding: hide
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyverse)
```
# Dataset

```{r raw-df}
raw_df <- readRDS("H:\\My Drive\\R\\Exercise Files\\rp_201801_202005_df.rds")

str(raw_df)
```

# Exercise 1

Find the **mean** and **standard deviation** of licensed geothermal productions in all years. (Tip: Use lubridate::year to get years from date data.)

```{r mean-sd}
raw_df %>%
  select(datetime = dt, geothermal_lic) %>%
  group_by(year = lubridate::year(datetime)) %>%
  summarize(mean_geo = mean(geothermal_lic), 
            sd_geo = sd(geothermal_lic))
```

# Exercise 2

Find the **hourly average** unlicensed solar (sun_ul) production levels for May 2020.

``` {r avg-solar}
raw_df %>%
  mutate(hour = lubridate::hour(dt), month = lubridate::month(dt), year = lubridate::year(dt)) %>%
  filter(month == 5, year == 2020) %>%
  group_by(hour) %>%
  summarize(hourly_avg = mean(sun_ul)) %>%
  select(hour, avg_prod = hourly_avg)

```

# Exercise 3

Find the **average daily percentage** change of licensed biomass (biomass_lic) in 2019. (e.g. Suppose daily production is 50 in day 1 and 53 in day 2, then the change should be (53-50)/50 -1 = 0.06) (Tip: Use lubridate::as_date to convert date time to date. Use lag and lead functions to offset values.)

```{r percent-biomass}
raw_df %>%
  mutate(date = lubridate::as_date(dt), 
         year = lubridate::year(dt)) %>%
  filter(year == 2019) %>%
  group_by(date) %>%
  summarize(sum_bio = sum(biomass_lic)) %>%
  transmute(date, sum_bio,
            daily_sum_next = lead(sum_bio,1), percent_daily = (daily_sum_next - sum_bio) / sum_bio) %>%
  summarize(avg_change = mean(percent_daily, na.rm=TRUE))

```

# Exercise 4

Find the **yearly total production levels** in TWh (Current values are in MWh. 1 GWh is 1000 MWh and 1 TWh is 1000 GWh). (Tip: In order to avoid a lengthy summation you can use tidyr::pivot_longer to get a long format.)


```{r yearly-total-prod}

raw_df %>%
  mutate(year=lubridate::year(dt)) %>%
  select(-dt) %>%
  pivot_longer(-year) %>%
  group_by(year) %>%
  summarise(total_production = sum(value)/10^6)

```
