---
title: "Reporting with R Markdown"
author: "Mine Kara"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
  html_document:
    # css: styles.css --> if we want to add css file we can add ths code here.
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: true
params:
  country: Turkey
  year_start: 2017-07-01
  year_end: 2018-06-30
  fy: 2018
---

<style>

#TOC {
  color: #708090;
  font-family: Calibri;
  font-size: 16px;
  border-color: #708090;
}

#h1.title {
  color: #F08080;
  background-color: #F5F5F5
  opacity: 0.6;
  font-family: Calibri;
  font-size: 20px;
}

#h4.date {
  color: #708090;
  font_family: Calibri;
  background-color: #F5F5F5
}

#h4.author {
  color: #708090;
  font_family: Calibri;
  background-color: #F5F5F5
}

body {
  color: #708090;
  font-family: Calibri;
  background-color: #F5F5F5;
}
pre {
  color: #708090;
  background-color: #F8F8FF;
}

</style>

<!-- To modify an option globally, pass it to knitr::opts_chunk$set() in the setup code chunk. -->
```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center", out.width = "80%",echo = TRUE)
```

<!-- include = FALSE -> Codes and results does not appear in the report when we knit the file -->
<!-- echo = FALSE -> Only Codes does not appear in the report when we knit the file -->
<!-- eval = FALSE -> The eval option specifies Whether or not we want to evaluate the code in a code chunk. If we want to exclude the code chunk from the report we can use it. Code will not run. -->
<!-- collapse = FALSE -> the code and any output appear in the knit file in separate block. -->


<!-- message = FALSE -> messages will not be shown. -->
<!-- warning = FALSE -> warnings will not be shown. -->
<!-- error = TRUE -> errors will be shown. -->

```{r data, include = FALSE}   
library(readr)
library(dplyr)
library(ggplot2)
library(knitr)


# setwd("H:/My Drive/R/R Markdown/Reporting R Markdown Files") Change working directory!!!


investment_annual_summary <- read_csv("H:\\My Drive\\R\\R Markdown\\Reporting R Markdown Files\\investment_annual_summary.csv")
investment_services_projects <- read_csv("H:\\My Drive\\R\\R Markdown\\Reporting R Markdown Files\\investment_services_projects.csv")
investment_region_summary <- read_csv("H:\\My Drive\\R\\R Markdown\\Reporting R Markdown Files\\investment_region_summary.csv")
```


# Datasets 

## Investment Annual Summary

The `investment_annual_summary` dataset provides a summary of the dollars in millions provided to each region for each fiscal year, from 2012 to 2018.

- Region
  - East Asia and the Pacific
  - Europe and Central Asia
  - Latin America and the Caribbean
  - Middle East and North Africa
  - South Asia
  - Sub-Saharan 

- Region
  1. East Asia and the Pacific
  2. Europe and Central Asia
  3. Latin America and the Caribbean
  4. Middle East and North Africa
  5. South Asia
  6. Sub-Saharan Africa


```{r investment-annual-summary, out.width = "85%", fig.cap = "'Figure 1.1 The Investment Annual Summary for each region for 2012 to 2018'"}
investment_annual_summary


ggplot(investment_annual_summary, aes(x= fiscal_year, y= dollars_in_millions, color = region)) +
geom_line() +
  labs(
    title = "Investment Annual Summary",
    x = "Fiscal Year",
    y = "Dollars in Millions"
  )
```


```{r tables}
kable(investment_region_summary, col.names = c("Region", "Dollars in Millions"), align = "cc", caption = "Table 1.1 The total investment summary for each region for the 2012 to 2018 fiscal years.")
```

## Investment Projects in `r params$country` in `r params$fy`

```{r country-annual-investment-projects, out.width = "95%", fig.cap = "'Figure 1.2 The Investment Services Projects in `r params$country` in 2018'", warning = FALSE}
country_annual_investment_projects <- investment_services_projects %>%
  filter(country == params$country,
         date_disclosed >= params$year_start,
         date_disclosed <= params$year_end) 

country_annual_investment_projects

country_annual_investment_projects_total <- country_annual_investment_projects %>%
  summarize(sum_total_investment = sum(total_investment, na.rm = TRUE)) 


ggplot(country_annual_investment_projects, aes(x = date_disclosed, y = total_investment, color = status)) +
  geom_point() +
  labs(
    title = "Investment Services Projects in `r params$country` in `r params$fy`",
    x = "Date Disclosed" ,
    y = "Total IFC Investment in Dollars in Millions"
  ) 
```

The total investment amount for all projects in `r params$country` in the `r params$fy` fiscal year was `r country_annual_investment_projects_total` million dollars.


## Investment Projects in Brazil

The `investment_services_projects` dataset provides information about each investment project from 2012 to 2018. Information listed includes the project name, company name, sector, project status, and investment amounts.

```{r brazil-investment-projects, out.width = "95%",fig.cap = "'Figure 1.3 The Investment Services Projects in Brazil from 2012 to 2018'", warning = FALSE}
 brazil_investment_projects <- investment_services_projects %>%
  filter(
    country == "Brazil"
  )

brazil_investment_projects


ggplot(brazil_investment_projects, aes(x=date_disclosed, y= total_investment, color=status)) +
  geom_point() +
  labs(
    title = "Investment Services Projects in Brazil",
    x = "Date Disclosed",
    y = "Total IFC Investment in Dollars in Millions")
```


## Investment Projects in Brazil in 2018

```{r brazil-investment-projects-2018, out.width = "95%", fig.cap = "'Figure 1.4 The Investment Services Projects in Brazil in 2018'", warning = FALSE}
brazil_investment_projects_2018 <- investment_services_projects %>%
  filter(country == "Brazil",
         date_disclosed >= "2017-07-01",
         date_disclosed <= "2018-06-30") 

brazil_investment_projects_2018

brazil_investment_projects_2018_total <- brazil_investment_projects_2018 %>%
  summarize(sum_total_investment = sum(total_investment, na.rm = TRUE)) 


ggplot(brazil_investment_projects_2018, aes(x = date_disclosed, y = total_investment, color = status)) +
  geom_point() +
  labs(
    title = "Investment Services Projects in Brazil in 2018",
    x = "Date Disclosed" ,
    y = "Total IFC Investment in Dollars in Millions"
  ) 
```

The total investment amount for all projects in Brazil in the 2018 fiscal year was `r brazil_investment_projects_2018_total` million dollars.